Parameters estimation via HOSVD

### 2025-08-17 Code/R/Research/HOSVD parameters estimate.Rmd
Add CPD
CDAM comparisons

knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
```

# Функции для тензоризации SSA
```{r tensorization}
source(file = "./Research/TSSA.R")
```

@@

## Графики RRMSE
```{r}
pltnms <- c("_no_rates", "_small_eq_rates", "_large_eq_rates", "")
pn <- 4

@@

```{r}
freq1.df <- freq1.rrmse |> as.data.frame() |> 
   mutate(dims = factor(x = apply(tens.dims, 1, paste, collapse = "x"),
                       levels = apply(tens.dims, 1, paste, collapse = "x"))) |>
  pivot_longer(!dims, names_to = "estim dim", names_prefix = "V", values_to = "RRMSE")

freq1.plot <- freq1.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RRMSE,
    group = `estim dim`,
    colour = `estim dim`,
    linetype = `estim dim`
  ), lwd = 1.2) + 
  geom_abline(
    slope = 0,
    intercept = min.ssa.rrmse$freq1[1],
    col = "gray10",
    lty = 3
  ) +
  annotate(
    geom = "text",
    x = 7,
    y = min.ssa.rrmse$freq1[1] * 0.95,
    label = paste0("ESPRIT min RRMSE, L=", min.ssa.rrmse$freq1[2])
  ) +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  freq1.plot,
  paste0("./img/freq1_dims", pltnms[pn], ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

```{r}
freq2.df <- freq2.rrmse |> as.data.frame() |> 
   mutate(dims = factor(x = apply(tens.dims, 1, paste, collapse = "x"),
                       levels = apply(tens.dims, 1, paste, collapse = "x"))) |>
  pivot_longer(!dims, names_to = "estim dim", names_prefix = "V", values_to = "RRMSE")

freq2.plot <- freq2.df |> ggplot() +
  geom_line(aes(
    x = dims,
    y = RRMSE,
    group = `estim dim`,
    colour = `estim dim`,
    linetype = `estim dim`
  ), lwd = 1.2) + 
  geom_abline(
    slope = 0,
    intercept = min.ssa.rrmse$freq2[1],
    col = "gray10",
    lty = 3
  ) +
  annotate(
    geom = "text",
    x = 7,
    y = min.ssa.rrmse$freq2[1] * 0.95,
    label = paste0("ESPRIT min RRMSE, L=", min.ssa.rrmse$freq2[2])
  ) +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  freq2.plot,
  paste0("./img/freq2_dims", pltnms[pn], ".pdf"),
  pdf,
  width = 9,
  height = 6,
  save = save
)
```

>>>>

setwd(rprojroot::find_rstudio_root_file())
knitr::opts_knit$set(root.dir = getwd())
source(file = "./Research/TSSA.R")
```

@@

## Графики RRMSE
```{r}
pltnms <- c("_no_rates", "_small_eq_rates", "_large_eq_rates", "")
pn <- 1

@@

```{r}
freq1.df <- freq1.rrmse |> as.data.frame() |>
  mutate(dims = factor(
    x = apply(tens.dims, 1, paste, collapse = "x"),
    levels = apply(tens.dims, 1, paste, collapse = "x")
  )) |>
  pivot_longer(
    !dims,
    names_to = "Estimation\nDimension",
    names_prefix = "V",
    values_to = "RRMSE"
  )

freq1.plot <- freq1.df[-(1:(2 * 3)), ] |> ggplot() +
  geom_line(
    aes(
      x = dims,
      y = RRMSE,
      group = `Estimation\nDimension`,
      colour = `Estimation\nDimension`,
      linetype = `Estimation\nDimension`
    ),
    lwd = 1.2
  ) +
  geom_abline(
    slope = 0,
    intercept = min.ssa.rrmse$freq1[1],
    col = "gray10",
    lty = 3
  ) +
  annotate(
    geom = "text",
    x = 7,
    y = min.ssa.rrmse$freq1[1] * 0.95,
    label = paste0("ESPRIT min RRMSE, L=", min.ssa.rrmse$freq1[2])
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  freq1.plot,
  paste0("./img/freq1_dims", pltnms[pn], ".pdf"),
  pdf,
  width = 11,
  height = 5,
  save = save
)
```

```{r}
freq2.df <- freq2.rrmse |> as.data.frame() |>
  mutate(dims = factor(
    x = apply(tens.dims, 1, paste, collapse = "x"),
    levels = apply(tens.dims, 1, paste, collapse = "x")
  )) |>
  pivot_longer(
    !dims,
    names_to = "estim dim",
    names_prefix = "V",
    values_to = "RRMSE"
  )

freq2.plot <- freq2.df[-(1:(2*3)), ]  |> ggplot() +
  geom_line(
    aes(
      x = dims,
      y = RRMSE,
      group = `estim dim`,
      colour = `estim dim`,
      linetype = `estim dim`
    ),
    lwd = 1.2
  ) +
  geom_abline(
    slope = 0,
    intercept = min.ssa.rrmse$freq2[1],
    col = "gray10",
    lty = 3
  ) +
  annotate(
    geom = "text",
    x = 7,
    y = min.ssa.rrmse$freq2[1] * 0.95,
    label = paste0("ESPRIT min RRMSE, L=", min.ssa.rrmse$freq2[2])
  ) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90))

plot.save(
  freq2.plot,
  paste0("./img/freq2_dims", pltnms[pn], ".pdf"),
  pdf,
  width = 11,
  height = 5,
  save = save
)
```
